### 2022-08-12 editorial-materials/EPB-2022-0116_response_to_reviewer.Rmd

---
title: "A geo-referenced micro-data set of real estate listings for Spain’s three largest cities - Response to referees"
output: pdf_document
---

### 2022-08-12 EPB/main_EPB.tex
Revisions complete for resubmission to EPB

\runninghead{Rey-Blanco \emph{et al}.}

@@

We are also witnessing a growing interest in open data in geography and
data science \citep{arribasl2021editorial, arribas2021} using
reproducible or replicable research \citep{paez2021open}. But to work
openly in science, it is necessary to have free software and open data.
While great efforts have been made to make free software available to
researchers (e.g., R or Python), not much data is currently out in the
open. In the particular case of the real estate market, to our
knowledge, there are few open micro-data sets of housing markets
available \citep{Song2021}.

To overcome these limitations, this paper presents a sort description of
an open micro-data set of geo-referenced dwelling listings. The data
have been provided by the Idealista
company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal}
and contain information about 189,923 dwellings located in Spain's three
largest cities. To date, this data product is the biggest open
geo-referenced micro-data set of the housing market in Spain. Moreover,
the data set has been supplied directly by Idealista, and therefore is
clean and free of download errors. The listings have been enriched with
official information from the Spanish cadastre along with other relevant
geographical features, such as distance to urban points of interest. The
data set is distributed as an R package, named `idealista18', which can
be accessed from the Github repository.

@@

The open data set `idealista18' is an R package composed of nine
objects, three objects for each of the three main Spanish cities:
Barcelona, Madrid, and Valencia. For each city, dwelling listings,
neighborhood polygons, and a set of points of interest have been
included in the R package. The following subsections describe each
object. A full description of the data is available in the help section
of the package.

@@

>>>>

\runninghead{author \emph{et al}.}

@@

We are also witnessing a growing interest in open data in geography and
data science \citep{arribasl2021editorial, arribas2021} using
reproducible or replicable research
\citep{paez2021open, brunsdon2021opening}. But to work openly in
science, it is necessary to have free software and open data. While
great efforts have been made to make free software available to
researchers (e.g., R or Python), data regarding real estate markets tend
to be treated as confidential, and there are still few open micro-data
sets of housing markets available \citep{Song2021}.

To contribute to the growing inventory of international micro-data sets
of real estate markets, this paper introduces an open micro-data set of
geo-referenced dwelling listings. The data have been provided by the
Idealista
company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal}
and contain information about 189,923 dwellings located in Spain's three
largest cities. To date, this data product is the biggest open
geo-referenced micro-data set of the housing market in Spain. Moreover,
the data set has been supplied directly by Idealista, and therefore is
clean and free of download errors. However, in order to be able to share
publicly the data we have slightly modified some variables by applying
some random noise which will not bias the main results derived from its
usage.

This micro-data set is expected to be used as a benchmark dataset to
test empirical methods in a reproducible fashion. Applied and
theoretical researchers on real estate mass appraisal and valuation
methods might use this dataset to canonically compare the performance of
their proposed comparable and hedonic models, among others. The data can
also be used to study the segmentation of housing submarkets and related
topics such as the impact of suburban areas on house prices. The
listings have been enriched with official information from the Spanish
cadastre along with other relevant geographical features, such as
distance to urban points of interest. In any case, the data might be
easily extended by spatially joining other datasets that contain
information at administrative, census tract, or postal code levels.

The data set is distributed as an R package, name \{idealista18\}, which
can be accessed from a public Github
repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}.
The database idealista18 is made available under the
\href{http://opendatacommons.org/licenses/odbl/1.0/}{Open Database License}.
For transparency, we also share the randomisation process applied to the
original data in the aforementioned Github repository.

@@

The open data product \{idealista18\} is an R package composed of nine
objects, three objects for each of the three main Spanish cities:
Barcelona, Madrid, and Valencia. For each city, dwelling listings,
neighborhood polygons, and a set of points of interest have been
included in the R package. The following subsections describe each
object. A full description of the data is available in the help section
of the package. We have strived to the best of our ability to comply
with FAIR principles regarding research data \citep{Wilkinson2016fair}:
upon publication, the dataset has a persistent digital object
identifier; publication as a data article makes the data findable; the
data and metadata are packaged together and protocols for help files in
the R ecosystem mean that documentation is easily searchable;
distribution as an R package means that only open software is needed to
access the data; and a public repository documents all data processes
followed to generate the distributed open data product.

@@

\hypertarget{declaration-of-competing-interest}{%
\section{Declaration of Competing
Interest}\label{declaration-of-competing-interest}}

Author One and author Two are employed by Idealista. They have been
granted permission to share the data presented in this article. None of
the authors have financial interests or personal relationships which
have, or could be perceived to have, influenced the work reported in
this article.

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

The authors wish to thank Alessandro Galesi for their support in the
paper revision and Juan Ramón Selva for collecting and cleaning the
spatial data. This work has been partially funded by the Spanish
Ministry of Economy and Competitiveness Grants PID2019-107800GB-100

### 2022-08-12 README.Rmd
Revisions complete for resubmission to EPB

<!-- badges: start -->
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-ODbLv1.0-blue.svg)](https://opendatacommons.org/licenses/odbl/1-0/)

>>>>

<!-- badges: start -->
[![License: ODbLv1.0](https://img.shields.io/badge/license-ODbLv1.0-blue.svg)](https://opendatacommons.org/licenses/odbl/1-0/)
